Typed Functional Genetic Programming

### 2013-06-25 tex/thesis.tex
[tex] little bit more on A*

A* is a general informed search algorithm used for finding shortest path in a state space.
According to \cite{AIAMA} A* is the most widely known form of best-first search.

>>>>

A* is a general informed search algorithm used for finding least-cost 
path from a given initial state to some goal state in a state space.
According to \cite{AIAMA} A* is the most widely known form of best-first search.

As A* traverses the state space, it follows a path of the lowest expected total cost.
It uses a priority queue of alternative unfinished paths.

...\\\\\\\\
\textbf{TODO : čeknout jak je to v kódu jestli ten A* co tam je čekuje ty
 nódy co už navštívil při přidávání
}
